### 2013-12-28 thesis/src/chapters/chapter-5-design.tex
Thesis: stub hld overview

\chapterintro{ This chapter introduces the high-level design of Cloud-SAP.
  Further elaboration on the layers of the proposed platform is presented
  and detailed discussion about the each layer is held.
}

@@

Diagram \ref{design:hld-overview} illustrates exemplary Cloud-SAP deployment, among depicted components we can distinguish two main parts of proposed solution: auto-scaling subsystem and inter-cloud broker. Auto-scaling subsystem is responsible for scaling users' application, taking into account different scalability perspectives, handled by a different layers:
\begin{itemize}
	\item application platform layer: application platform tuning
	\item container layer: vertical scaling
	\item stack layer: horizontal scaling
	\item inter-cloud layer: scaling out across different cloud providers
\end{itemize}
The last mentioned layer - inter-cloud - cooperates with different cloud providers, hence, it requires additional work that has to be done. In fact, these extra tasks are delegated to a inter-cloud broker, responsible for a dialog in a cloud federation.

Diagram \ref{design:csap-layers} depicts that multi-layered structure.

@@

\subsubsection{Autonomic components}
Each layer of the Cloud-SAP (shown in figure \ref{design:csap-layers}) must be characterised by an ability to adapt to a given application usage. As the previous chapter stated, this can be achieved by adding an elasticity controller to each layer. This observation is a foundation of proposed architecture.

One of the first models that ensured system adaptivity is an autonomic component, concept based on a feed-back loop, initially proposed by IBM \cite{IBM06}. Figure \ref{design:autonomic-component} depicts that architecture.

@@

\subsubsection{Monitoring}
Monitoring module of each autonomic component aims to gather data from Sensors of a managed resource. While design of Cloud-SAP doesn't have any specific requirements regarding underlying monitoring mechanism there are a few aspects that should be taken into consideration. Table \ref{tab:monitoring-module-issues-summary} summarises main points.

@@

Cloud-SAP is entirely focused on further data processing, consequently whether to store monitoring data or not is entirely implementation dependant.

\subsubsection{Analysis}

\subsubsection{Planning}

\subsubsection{Execution}

\subsubsection{Knowledge base}

\subsubsection{Hierarchical autonomic-system}
Due to the fact that designed platform operates on multiple layers, we can extend idea of an autonomic component by using concept of a multi-hierarchical autonomic system \cite{LiWoZh05}. Figure \ref{design:hierarchical-autonomic-system} illustrates that hierarchy, were each level represents a different perspective on an application scaling. Using terminology characteristic to a autonomic system, first three hierarchy levels (application tuning, container, stack) are centralised and controlled by a single elasticity controller at each level, while the last inter-cloud level is a decentralized one - each cloud instance is fully independent.

Due to the hierarchy of our architecture, each level manages an underlying autonomic component, while being managed by an upper layer at the very same time.

>>>>

\chapterintro{ This chapter introduces the high-level design of Cloud-SAP, highlighting its core concepts and indicating possible implementation ideas.
}

@@

Diagram \ref{design:hld-overview} illustrates exemplary Cloud-SAP deployment, among depicted components we can distinguish two main parts of proposed solution: auto-scaling subsystem and inter-cloud broker. Auto-scaling subsystem is responsible for scaling users' application, taking into account different scalability perspectives, handled by a different layers:
\begin{itemize}
	\item application platform layer: application platform tuning
	\item container layer: vertical scaling
	\item stack layer: horizontal scaling
	\item inter-cloud layer: scaling out across different cloud providers
\end{itemize}
The last mentioned layer - inter-cloud - cooperates with different cloud providers, hence, it requires additional work to be done. In fact, these extra tasks are delegated to a inter-cloud broker, responsible for a dialog in a cloud federation.

@@

\subsubsection{Autonomic components}
Each layer of the Cloud-SAP (shown in figure \ref{design:csap-layers}) must be characterised by an ability to adapt to a given application usage. One of the first models that ensured system adaptivity is an autonomic component, concept based on a feed-back loop, initially proposed by IBM \cite{IBM06}. Figure \ref{design:autonomic-component} depicts that architecture. This observation is a foundation of proposed architecture - adaptivity is achieved by enriching each layer with an elasticity controller that is in fact an autonomic component.

@@

Due to the fact that designed platform operates on multiple layers, we can extend idea of an autonomic component by using concept of a multi-hierarchical autonomic system \cite{LiWoZh05}. Figure \ref{design:hierarchical-autonomic-system} illustrates that hierarchy, were each level represents a different perspective on an application scaling. First three hierarchy levels (application tuning, container, stack) are centralised and controlled by a single elasticity controller at each level, while the last inter-cloud level is a decentralized one - each cloud instance is fully independent.

Considering hierarchy of our architecture, each level manages an underlying autonomic component, while being managed by an upper layer at the very same time.

\subsubsection{Monitoring}
Monitoring module of each elasticity controller aims to gather data from \textit{Sensors} of a managed resource. While design of Cloud-SAP doesn't have any specific requirements regarding underlying monitoring mechanism, there are a few aspects that should be taken into consideration. Table \ref{tab:monitoring-module-issues-summary} summarises main points.

@@

Cloud-SAP is entirely focused on further data processing, consequently decision whether to store monitoring data or not is entirely implementation dependent.

\subsubsection{Analysis}
Analyse module applies a specified mathematical model to a gathered data and yields a conclusion on top of that. There is a vast number of models that can be used for that purpose, for example \cite{LiWoZh05} enumerates:
\begin{itemize}
 \item Queue-based Performance Models
 \item Dynamic models
 \item Monotonic static models
 \item Policy based models
\end{itemize}

It is vital that Cloud-SAP implementation use predictive approach \cite{JiPeLiCh11} and track changes \cite{ZhYaWo05} in a system, giving a solid foundation for a knowledge base that can contribute to a better data analysis in future.

\subsubsection{Planning}
Planning module is responsible for scheduling actions that have to be taken to solve problems reported by an earlier analysis. This may involve:
\begin{itemize}
 \item reserving some resources (for example to deploy a new virtual machine)
 \item handling situation where multiple entities compete about the resources (for example by a prioritization)
\end{itemize}

It is possible, however, that resolving issues is not possible at a current layer. It that case, the upper-layer is responsible for handling it.

\subsubsection{Execution}
It is expected that execution module manage resource by performing various operations on resource's effector. Each layer is characterised by different actions that can be taken, for example: application server reconfiguration, vertical or horizontal scaling.

\subsubsection{Knowledge base}
Knowledge base is represented as a set of rules, policies shared across autonomous components.
